---
title: "bly_2024_local"
author: "Shannon Rose Blair"
date: "2024-08-21"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = "/Users/skb/Documents/Documents_Local/shrimp/rad/bly_2024")
```

knitr::opts_knit$set(root.dir = "/Users/skb/Documents/Documents_Local/shrimp/rad/bly_2024")
library(snpR)
library(tidyverse)

#for more detailed annotations on the code, please see the Rmd for the rangewide dataset. Much of the code is replicated and the annotations are more in-depth.

```{r sacramento}
#define local name
popn="sacramento"

#import data
snp_meta_in <- paste0("bly_2024_",popn,".mafs")
sample_meta_in <- paste0("bly_2024_",popn,"_meta.txt")
gen <- read.delim(paste0("bly_2024_",popn,".geno"), header=FALSE)
sm<- read.delim(snp_meta_in)
snp_meta <- sm[,1:4]
rm(sm)
gen <- gen[,3:(ncol(gen)-1)]
samp_meta <- read.delim(sample_meta_in,header=TRUE)

#format as snpR
pop <- import.snpR.data(gen,sample.meta = samp_meta,snp.meta = snp_meta ,mDat = "NN")

##filter
pop_hofilt <- filter_snps(x=pop, hf_hets = 0.6, min_ind=0.5,non_poly=FALSE)

pop_elsefilt <- filter_snps(x = pop, maf = 0.05, hf_hets = 0.6, min_ind =  0.8, min_loci = 0.5, re_run = "partial", non_poly = TRUE, bi_al = TRUE) 

##diversity##
##

pop_hofilt <- calc_pi(pop_hofilt, "Population")
pop_hofilt <- calc_ho(pop_hofilt, "Population")
pop_hofilt <- calc_he(pop_hofilt, "Population")
pop_hofilt <- calc_private(pop_hofilt, "Population")
pop_hofilt <- calc_tajimas_d(pop_hofilt, "Population.chromo",sigma=50,step=25)
stats <- get.snpR.stats(pop_hofilt, "Population", stats = c("pi", "ho", "he")) 
thetas <- get.snpR.stats(pop_hofilt, "Population.chromo", stats="tajimas_d")

#format and prep for graphics
basin_divmeans <- stats$weighted.means
basin_divmeans$ho_aut <- basin_divmeans$weighted_mean_ho / nsnps(pop_hofilt)
basin_divmeans$he_aut <- basin_divmeans$weighted_mean_he / nsnps(pop_hofilt)
basin_thetas <- filter(thetas$weighted.means,snp.subfacet==".OVERALL_MEAN")

all_thetas <- thetas$single.window
all_thetas$wst_persite <- all_thetas$ws.theta / all_thetas$n_snps
all_thetas$tst_persite <- all_thetas$ts.theta / all_thetas$n_snps
all_thetas$D <- as.numeric(all_thetas$D)
mean_thetas <- all_thetas %>% group_by(subfacet) %>% filter(n_snps>1000) %>% summarise(Taj_D=mean(D),mean_ttheta_persite=mean(tst_persite),sd_ttheta_persite=sd(tst_persite),mean_wtheta_persite=mean(wst_persite),sd_wtheta_persite=sd(wst_persite))

#write the summary
write_delim(mean_thetas,file=paste0(popn,"_mean_diversity_values.txt"),delim="\t",quote="none")
write_delim(basin_divmeans,file=paste0(popn,"_mean_ho_diversity.txt"),delim="\t",quote="none")
write_delim(all_thetas,paste0(popn,"thetas_raw.txt"),delim="\t",quote="none")
write_delim(basin_thetas,paste0(popn,"_mean_tajD.txt"),delim="\t",quote="none")

ts2 <- pivot_longer(all_thetas, cols=c(16,17),values_to="theta", names_to="Theta_Measure")
ts2$Theta_Measure[ts2$Theta_Measure=="tst_persite"] <- "Tajima's Theta"
ts2$Theta_Measure[ts2$Theta_Measure=="wst_persite"] <- "Watterson's Theta"
ylim1 = boxplot.stats(ts2$theta)$stats[c(1, 5)]

ts2 %>% filter(n_snps>1000) %>% ggplot(aes(x=subfacet,y=theta,fill=Theta_Measure)) + geom_boxplot(outlier.alpha=0.01) + coord_cartesian(ylim = ylim1*1.05) + xlab("Population") + ylab("Theta Diversity Value, Sliding Window") + theme_minimal() + theme(axis.text=element_text(angle = 90, vjust = 0.5, hjust=1)) + theme(text=element_text(size=20)) + fill_palette(c("#2ca25f",	"#99d8c9")) + theme(text=element_text(size=20,family="open sans"), axis.text = element_text(size=20),axis.title=element_text(size=20),legend.text = element_text(size=20),legend.title=element_text(size=20))

ggsave(paste0(popn,"_diversity_thetas_boxplots.png"),device="png",dpi=300)

ts2 %>% filter(n_snps>1000) %>% ggplot(aes(x = theta, y = subfacet, fill = subfacet)) + geom_density_ridges() + theme_ridges(font_size=20,) + theme(legend.position = "none",) + xlab("Per-Site Theta Values") +ylab("Population") + fill_palette(c("forestgreen","turquoise","orchid","#BD0026")) + xlim(c(-0.005,0.06)) + theme(text=element_text(size=20,family="open sans"), axis.text = element_text(size=18),axis.title=element_text(size=18),legend.text = element_text(size=18),legend.title=element_text(size=18)) + facet_wrap(facets="Theta_Measure")

ggsave(paste0(popn,"_diversity_thetas_ridgeline.png"),device="png",dpi=300)


##calculate smoothed averages##
sliding_ho <- calc_smoothed_averages(x = pop_hofilt, facets = "Population", sigma = 50, step =25)
sliding_ho_stats <- get.snpR.stats(sliding_ho, facets="Population",stats=c("ho","pi"))
single_ho <- sliding_ho_stats$single.window
single_pi <- sliding_ho_stats$single.window
#divide by number of interrogated sites for autosomal ho
single_ho$auto_ho <- single_ho$ho/single_ho$n_snps

single_ho %>% ggplot(aes(x = auto_ho, y = subfacet, fill = subfacet)) + geom_density_ridges() + theme_ridges(font_size=20) + theme(legend.position = "none",text=element_text(family="open sans",size=20)) + xlab("Observed Heterozygosity") +ylab("Population") + fill_palette(c("forestgreen","turquoise","orchid","#BD0026")) + xlim(c(0,0.000007))

ggsave(paste0(popn,"_diversity_ho_ridgeline.png"),device="png",dpi=300)

###ibd
##

pop2 <- calc_isolation_by_distance(
  pop_elsefilt,
  facets = "Population",
  x_y = c("long", "lat"),
  genetic_distance_method = "Edwards",
  interpolate = "bernoulli",
)

ibd2 <- get.snpR.stats(pop2, "Population", stats=c("isolation_by_distance","geographic_distance"))

ibd2

###Fst
fst <- calc_pairwise_fst(pop_elsefilt, facets="Population")
fst2 <- get.snpR.stats(fst,"Population",stats="fst")

plot_pairwise_fst_heatmap(fst,facets="Population",viridis.option="mako",lab_lower=TRUE) + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) + theme(text=element_text(size=22,family="open sans"),axis.title=element_text(size=1)) + geom_label(ggplot2::aes(label = round(weighted_mean_fst, 3), x = p2, y = p1), fill = "white",size=14, family="open sans")

ggsave(paste0(popn,"_fst_table.png"),device="png",dpi=300)

sac_m <- unique(data.frame("Population"=samp_meta$Population,"long"=samp_meta$long,"lat"=samp_meta$lat))
sac_m <- sac_m[-5,]
d1 <- geodist(sac_m,paired=TRUE,measure = "geodesic")
#turn matrix into pairwise
colnames(d1) <- sac_m$Population
row.names(d1) <- sac_m$Population
d1 <- as.data.frame(d1)
xy <- t(combn(colnames(d1), 2))
dists <- data.frame(xy, dist=d1[xy])
dists$subfacet <- paste0(dists$X1,"~",dists$X2)
dists2 <- dists
dists2$subfacet <- paste0(dists$X2,"~",dists$X1)
sacramento_dists <- rbind(dists,dists2)

#I want it in km, rather than m, so divide by 1000
sacramento_dists$dist_km <- dists$dist / 1000

sac_fst_dist <- fst2$weighted.means
sac_fst_dist <- left_join(sac_fst_dist,sacramento_dists,by="subfacet")
sac_fst_dist$t_geodist <- log(sac_fst_dist$dist_km) #take the natural log
sac_fst_dist$t_fst <- sac_fst_dist$weighted_mean_fst/(1-sac_fst_dist$weighted_mean_fst)


###PCA###
pc <- plot_clusters(pop_elsefilt,facets="Population")
pca <- pc$data$pca
popname <- str_to_title(popn)
 
ggplot2::ggplot(pca, aes(PC1, PC2, fill=Population)) + geom_point(shape=21,size=8,stroke=1) +xlab(paste0("PC1 (",pc$pca_loadings[1],"%)")) + ylab(paste0("PC2 (",pc$pca_loadings[2],"%)")) +ggtitle(paste0("VPFS ",popname, " Intra-Site Analysis: All Loci PC1-PC2")) +fill_palette(c("forestgreen","turquoise","orchid","#BD0026")) + theme_minimal() +theme(text=element_text(size=22,family="open sans")) 

ggsave(paste0(popn,"_pca_pc1vpc2.png"),device="png",dpi=300)

ggplot2::ggplot(pca, aes(PC1, PC3, fill=Population)) + geom_point(shape=21,size=8,stroke=1) +xlab(paste0("PC1 (",pc$pca_loadings[1],"%)")) + ylab(paste0("PC3 (",pc$pca_loadings[3],"%)")) +ggtitle(paste0("VPFS ",popname, " Intra-Site Analysis: All Loci PC1-PC3")) +fill_palette(c("forestgreen","turquoise","orchid","#BD0026")) +theme_minimal() +theme(text=element_text(size=22,family="open sans")) 

ggsave(paste0(popn,"_pca_pc1vpc3.png"),device="png",dpi=300)

###reformat for Bayesass###
pop_morefilt <- filter_snps(x = pop,maf = 0.05, hf_hets = 0.6,min_ind =  0.99, min_loci = 0.5, re_run = "partial", non_poly = TRUE, bi_al = TRUE)

pop_forbayes <- as.data.frame(pop_morefilt)
pop_fb_samp <- sample.meta(pop_morefilt)
pop_fb_snps <- snp.meta(pop_morefilt)
pop_fb_snps$chr_pos <- paste0(pop_fb_snps$chromo,"_",pop_fb_snps$position)
rownames(pop_forbayes) <- pop_fb_snps$chr_pos
colnames(pop_forbayes) <- pop_fb_samp$sample
pop_forbayes$allele <- rownames(pop_forbayes)
test2 <- data.frame(pop_forbayes)
test3 <- pivot_longer(test2, cols=c(1:(ncol(test2)-1)),names_to="sample")
test4 <- right_join(samp_meta,test3,by="sample")
test4$a1 <- str_split_i(test4$value,"",1)
test4$a2 <- str_split_i(test4$value,"",2)
test4$a1[test4$a1 =="N"] <- 0
test4$a2[test4$a2 =="N"] <- 0
test5 <- data.frame("indID"=test4$sample,"PopulationID"=test4$Population,"locID"=test4$allele,"allele1"=test4$a1,"allele2"=test4$a2)
write_delim(test5,paste0(popn,"_for_ba3_snpr.txt"),delim=" ")
##

df2 <- data.frame(pop_elsefilt)
df3 <- as.data.frame(t(df2))
row.names(df3) <- sample.meta(pop_elsefilt)$sample
colnames(df3) <- paste0(snp.meta(pop_elsefilt)$chromo,"_",snp.meta(pop_elsefilt)$position)
t1 <- df2genind(df3, pop=sample.meta(pop_elsefilt)$Population,ncode=2,NA.char="NN")
X <- tab(t1, NA.method="mean")
D <- dist(X)
tre <- nj(D)
h2 <- c("forestgreen","turquoise","orchid","#BD0026")
myCol <- h2[as.integer(pop(t1))]
par(bg = "white",family="open sans")
plot(tre, type = "unr", show.tip.lab = FALSE)
tiplabels(col = "black", pch = 21, bg=myCol,cex=3.5)
poplist <- c("Cook","Kiefer","Werre","Werre_B")
mylegcol <- unique(myCol)
legend(-30,180,legend=poplist, fill=mylegcol, cex=1, title="Population", bty="n")

library("ape")
df2 <- data.frame(pop_elsefilt)
df3 <- as.data.frame(t(df2))
row.names(df3) <- sample.meta(pop_elsefilt)$sample
colnames(df3) <- paste0(snp.meta(pop_elsefilt)$chromo,"_",snp.meta(pop_elsefilt)$position)
t1 <- df2genind(df3, pop=sample.meta(pop_elsefilt)$Population,ncode=2,NA.char="NN")
X <- tab(t1, NA.method="mean")
D <- dist(X)
tre <- nj(D)
h2 <- c("forestgreen","turquoise","orchid","#BD0026")
myCol <- h2[as.integer(pop(t1))]
par(bg = "white",family="open sans")
plot(tre, type = "unr", show.tip.lab = FALSE)
tiplabels(col = "black", pch = 21, bg=myCol,cex=3.5)
poplist <- c("Cook","Kiefer","Werre","Werre_B")
mylegcol <- unique(myCol)
legend(-30,120,legend=poplist, fill=mylegcol, cex=1, title="Population", bty="n")
ggsave(paste0(popn,"_njtree.png"), device="png", dpi=200)
```

```{r merced}
#define local name
popn="merced"
setwd("~/Documents/Documents_Local/shrimp/rad/bly_2024")
#import data
snp_meta_in <- paste0("bly_2024_",popn,".mafs")
sample_meta_in <- paste0("bly_2024_",popn,"_meta.txt")
gen <- read.delim(paste0("bly_2024_",popn,".geno"), header=FALSE)
sm<- read.delim(snp_meta_in)
snp_meta <- sm[,1:4]
rm(sm)
gen <- gen[,3:(ncol(gen)-1)]
samp_meta <- read.delim(sample_meta_in,header=TRUE)

#format as snpR
pop <- import.snpR.data(gen,sample.meta = samp_meta,snp.meta = snp_meta ,mDat = "NN")

##filter
pop_hofilt <- filter_snps(x=pop, hf_hets = 0.6, min_ind=0.5,non_poly=FALSE)

pop_elsefilt <- filter_snps(x = pop, maf = 0.05, hf_hets = 0.6, min_ind =  0.8, min_loci = 0.5, re_run = "partial", non_poly = TRUE, bi_al = TRUE) 

##diversity##
##

pop_hofilt <- calc_pi(pop_hofilt, "Population")
pop_hofilt <- calc_ho(pop_hofilt, "Population")
pop_hofilt <- calc_he(pop_hofilt, "Population")
pop_hofilt <- calc_private(pop_hofilt, "Population")
pop_hofilt <- calc_tajimas_d(pop_hofilt, "Population.chromo",sigma=50,step=25)
stats <- get.snpR.stats(pop_hofilt, "Population", stats = c("pi", "ho", "he")) 
thetas <- get.snpR.stats(pop_hofilt, "Population.chromo", stats="tajimas_d")

#format and prep for graphics
basin_divmeans <- stats$weighted.means
basin_divmeans$ho_aut <- basin_divmeans$weighted_mean_ho / nsnps(pop_hofilt)
basin_divmeans$he_aut <- basin_divmeans$weighted_mean_he / nsnps(pop_hofilt)
basin_thetas <- filter(thetas$weighted.means,snp.subfacet==".OVERALL_MEAN")

all_thetas <- thetas$single.window
all_thetas$wst_persite <- all_thetas$ws.theta / all_thetas$n_snps
all_thetas$tst_persite <- all_thetas$ts.theta / all_thetas$n_snps
all_thetas$D <- as.numeric(all_thetas$D)
mean_thetas <- all_thetas %>% group_by(subfacet) %>% filter(n_snps>1000) %>% summarise(Taj_D=mean(D),mean_ttheta_persite=mean(tst_persite),sd_ttheta_persite=sd(tst_persite),mean_wtheta_persite=mean(wst_persite),sd_wtheta_persite=sd(wst_persite))

#write the summary
write_delim(mean_thetas,file=paste0(popn,"_mean_diversity_values.txt"),delim="\t",quote="none")
write_delim(basin_divmeans,file=paste0(popn,"_mean_ho_diversity.txt"),delim="\t",quote="none")
write_delim(all_thetas,paste0(popn,"thetas_raw.txt"),delim="\t",quote="none")
write_delim(basin_thetas,paste0(popn,"_mean_tajD.txt"),delim="\t",quote="none")

ts2 <- pivot_longer(all_thetas, cols=c(16,17),values_to="theta", names_to="Theta_Measure")
ts2$Theta_Measure[ts2$Theta_Measure=="tst_persite"] <- "Tajima's Theta"
ts2$Theta_Measure[ts2$Theta_Measure=="wst_persite"] <- "Watterson's Theta"
ylim1 = boxplot.stats(ts2$theta)$stats[c(1, 5)]

ts2 %>% filter(n_snps>1000) %>% ggplot(aes(x=subfacet,y=theta,fill=Theta_Measure)) + geom_boxplot(outlier.alpha=0.01) + coord_cartesian(ylim = ylim1*1.05) + xlab("Population") + ylab("Theta Diversity Value, Sliding Window") + theme_minimal() + theme(axis.text=element_text(angle = 90, vjust = 0.5, hjust=1)) + theme(text=element_text(size=20)) + fill_palette(c("#2ca25f",	"#99d8c9")) + theme(text=element_text(size=20,family="open sans"), axis.text = element_text(size=20),axis.title=element_text(size=20),legend.text = element_text(size=20),legend.title=element_text(size=20))

ggsave(paste0(popn,"_diversity_thetas_boxplots.png"),device="png",dpi=300)

ts2 %>% filter(n_snps>1000) %>% ggplot(aes(x = theta, y = subfacet, fill = subfacet)) + geom_density_ridges() + theme_ridges(font_size=20,) + theme(legend.position = "none",) + xlab("Per-Site Theta Values") +ylab("Population") + fill_palette(c("#FDBF6F","yellow1","gold2","sienna2","firebrick1","coral3","#F03B20","#FF7F00")) + xlim(c(-0.005,0.06)) + theme(text=element_text(size=20,family="open sans"), axis.text = element_text(size=18),axis.title=element_text(size=18),legend.text = element_text(size=18),legend.title=element_text(size=18)) + facet_wrap(facets="Theta_Measure")

ggsave(paste0(popn,"_diversity_thetas_ridgeline.png"),device="png",dpi=300)


##calculate smoothed averages##
sliding_ho <- calc_smoothed_averages(x = pop_hofilt, facets = "Population", sigma = 50, step =25)
sliding_ho_stats <- get.snpR.stats(sliding_ho, facets="Population",stats=c("ho","pi"))
single_ho <- sliding_ho_stats$single.window
single_pi <- sliding_ho_stats$single.window
#divide by number of interrogated sites for autosomal ho
single_ho$auto_ho <- single_ho$ho/single_ho$n_snps

single_ho %>% ggplot(aes(x = auto_ho, y = subfacet, fill = subfacet)) + geom_density_ridges() + theme_ridges(font_size=20) + theme(legend.position = "none",text=element_text(family="open sans",size=20)) + xlab("Observed Heterozygosity") +ylab("Population") + fill_palette(c("#FDBF6F","yellow1","gold2","sienna2","firebrick1","coral3","#F03B20","#FF7F00")) + xlim(c(0,0.000007))

ggsave(paste0(popn,"_diversity_ho_ridgeline.png"),device="png",dpi=300)

###ibd
##

pop2 <- calc_isolation_by_distance(
  pop_elsefilt,
  facets = "Population",
  x_y = c("long", "lat"),
  genetic_distance_method = "Edwards",
  interpolate = "bernoulli",
)

ibd2 <- get.snpR.stats(pop2, "Population", stats=c("isolation_by_distance","geographic_distance"))

ibd2

###Fst
fst <- calc_pairwise_fst(pop_elsefilt, facets="Population")
fst2 <- get.snpR.stats(fst,"Population",stats="fst")

plot_pairwise_fst_heatmap(fst,facets="Population",facet.order=c("Dutchman","Dutchman_B","Dutchman_C","UCMerced","UCM_B","UCM_C","UCM_D","UCM_E"),viridis.option="mako",lab_lower=TRUE) + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) + theme(text=element_text(size=22,family="open sans"),axis.title=element_text(size=1)) + geom_label(ggplot2::aes(label = round(weighted_mean_fst, 3), x = p2, y = p1), fill = "white",size=10, family="open sans")

ggsave(paste0(popn,"_fst_table.png"),device="png",dpi=300)

merced_m <- unique(data.frame("Population"=samp_meta$Population,"long"=samp_meta$long,"lat"=samp_meta$lat))
d1 <- geodist(merced_m,paired=TRUE,measure = "geodesic")
#turn matrix into pairwise
colnames(d1) <- merced_m$Population
row.names(d1) <- merced_m$Population
d1 <- as.data.frame(d1)
xy <- t(combn(colnames(d1), 2))
dists <- data.frame(xy, dist=d1[xy])
dists$subfacet <- paste0(dists$X1,"~",dists$X2)
dists2 <- dists
dists2$subfacet <- paste0(dists$X2,"~",dists$X1)
merced_dists <- rbind(dists,dists2)

#I want it in km, rather than m, so divide by 1000
merced_dists$dist_km <- dists$dist / 1000

merced_fst_dist <- fst2$weighted.means
merced_fst_dist <- left_join(merced_fst_dist,merced_dists,by="subfacet")
merced_fst_dist$t_geodist <- log(merced_fst_dist$dist_km) #take the natural log
merced_fst_dist$t_fst <- merced_fst_dist$weighted_mean_fst/(1-merced_fst_dist$weighted_mean_fst)


###PCA###
pc <- plot_clusters(pop_elsefilt,facets="Population")
pca <- pc$data$pca
popname <- str_to_title(popn)
 
ggplot2::ggplot(pca, aes(PC1, PC2, fill=Population)) + geom_point(shape=21,size=8,stroke=1) +xlab(paste0("PC1 (",pc$pca_loadings[1],"%)")) + ylab(paste0("PC2 (",pc$pca_loadings[2],"%)")) +ggtitle(paste0("VPFS ",popname, " Intra-Site Analysis: All Loci PC1-PC2")) +fill_palette(c("#FDBF6F","yellow1","gold2","sienna2","firebrick1","coral3","#F03B20","#FF7F00")) +theme_minimal() + theme(text=element_text(size=22,family="open sans")) 

ggsave(paste0(popn,"_pca_pc1vpc2.png"),device="png",dpi=300)

ggplot2::ggplot(pca, aes(PC1, PC3, fill=Population)) + geom_point(shape=21,size=8,stroke=1) +xlab(paste0("PC1 (",pc$pca_loadings[1],"%)")) + ylab(paste0("PC3 (",pc$pca_loadings[3],"%)")) +ggtitle(paste0("VPFS ",popname, " Intra-Site Analysis: All Loci PC1-PC3")) +fill_palette(c("#FDBF6F","yellow1","gold2","sienna2","firebrick1","coral3","#F03B20","#FF7F00")) +theme(text=element_text(size=22,family="open sans")) 

ggsave(paste0(popn,"_pca_pc1vpc3.png"),device="png",dpi=300)

###reformat for Bayesass###
pop_morefilt <- filter_snps(x = pop,maf = 0.05, hf_hets = 0.6,min_ind =  0.99, min_loci = 0.5, re_run = "partial", non_poly = TRUE, bi_al = TRUE)

pop_forbayes <- as.data.frame(pop_morefilt)
pop_fb_samp <- sample.meta(pop_morefilt)
pop_fb_snps <- snp.meta(pop_morefilt)
pop_fb_snps$chr_pos <- paste0(pop_fb_snps$chromo,"_",pop_fb_snps$position)
rownames(pop_forbayes) <- pop_fb_snps$chr_pos
colnames(pop_forbayes) <- pop_fb_samp$sample
pop_forbayes$allele <- rownames(pop_forbayes)
test2 <- data.frame(pop_forbayes)
test3 <- pivot_longer(test2, cols=c(1:(ncol(test2)-1)),names_to="sample")
test4 <- right_join(samp_meta,test3,by="sample")
test4$a1 <- str_split_i(test4$value,"",1)
test4$a2 <- str_split_i(test4$value,"",2)
test4$a1[test4$a1 =="N"] <- 0
test4$a2[test4$a2 =="N"] <- 0
test5 <- data.frame("indID"=test4$sample,"PopulationID"=test4$Population,"locID"=test4$allele,"allele1"=test4$a1,"allele2"=test4$a2)
write_delim(test5,paste0(popn,"_for_ba3_snpr.txt"),delim=" ")
##
##njtree

library("ape")
df2 <- data.frame(pop_elsefilt)
df3 <- as.data.frame(t(df2))
row.names(df3) <- sample.meta(pop_elsefilt)$sample
colnames(df3) <- paste0(snp.meta(pop_elsefilt)$chromo,"_",snp.meta(pop_elsefilt)$position)
t1 <- df2genind(df3, pop=sample.meta(pop_elsefilt)$Population,ncode=2,NA.char="NN")
X <- tab(t1, NA.method="mean")
D <- dist(X)
tre <- nj(D)
#levels(t1@pop) <- c("Dutchman","Dutchman_B","Dutchman_C","UCMerced","UCM_B","UCM_C","UCM_D","UCM_E")
h2 <-c("#F03B20","firebrick1","sienna2","coral3","#FF7F00","#FDBF6F","gold2","yellow1")
myCol <- h2[as.integer(pop(t1))]
par(bg = "white",family="open sans")
plot(tre, type = "unr", show.tip.lab = FALSE)
tiplabels(col = "black", pch = 21, bg=myCol,cex=3.5)
poplist <- levels(t1@pop)
mylegcol <- unique(myCol)
legend(-45,180,legend=poplist, fill=mylegcol, cex=1, title="Population", bty="n")

```

```{r oregon}
#define local name
popn="oregon"
#setwd("~/Documents/Documents_Local/shrimp/rad/bly_2024")
#import data
snp_meta_in <- paste0("bly_2024_",popn,".mafs")
sample_meta_in <- paste0("bly_2024_",popn,"_meta.txt")
gen <- read.delim(paste0("bly_2024_",popn,".geno"), header=FALSE)
sm<- read.delim(snp_meta_in)
snp_meta <- sm[,1:4]
rm(sm)
gen <- gen[,3:(ncol(gen)-1)]
samp_meta <- read.delim(sample_meta_in,header=TRUE)

#format as snpR
pop <- import.snpR.data(gen,sample.meta = samp_meta,snp.meta = snp_meta ,mDat = "NN")

##filter
pop_hofilt <- filter_snps(x=pop, hf_hets = 0.6, min_ind=0.5,non_poly=FALSE)

pop_elsefilt <- filter_snps(x = pop, maf = 0.05, hf_hets = 0.6, min_ind =  0.8, min_loci = 0.5, re_run = "partial", non_poly = TRUE, bi_al = TRUE) 

##diversity##
##

pop_hofilt <- calc_pi(pop_hofilt, "Population")
pop_hofilt <- calc_ho(pop_hofilt, "Population")
pop_hofilt <- calc_he(pop_hofilt, "Population")
pop_hofilt <- calc_private(pop_hofilt, "Population")
pop_hofilt <- calc_tajimas_d(pop_hofilt, "Population.chromo",sigma=50,step=25)
stats <- get.snpR.stats(pop_hofilt, "Population", stats = c("pi", "ho", "he")) 
thetas <- get.snpR.stats(pop_hofilt, "Population.chromo", stats="tajimas_d")

#format and prep for graphics
basin_divmeans <- stats$weighted.means
basin_divmeans$ho_aut <- basin_divmeans$weighted_mean_ho / nsnps(pop_hofilt)
basin_divmeans$he_aut <- basin_divmeans$weighted_mean_he / nsnps(pop_hofilt)
basin_thetas <- filter(thetas$weighted.means,snp.subfacet==".OVERALL_MEAN")

all_thetas <- thetas$single.window
all_thetas$wst_persite <- all_thetas$ws.theta / all_thetas$n_snps
all_thetas$tst_persite <- all_thetas$ts.theta / all_thetas$n_snps
all_thetas$D <- as.numeric(all_thetas$D)
mean_thetas <- all_thetas %>% group_by(subfacet) %>% filter(n_snps>1000) %>% summarise(Taj_D=mean(D),mean_ttheta_persite=mean(tst_persite),sd_ttheta_persite=sd(tst_persite),mean_wtheta_persite=mean(wst_persite),sd_wtheta_persite=sd(wst_persite))

#write the summary
write_delim(mean_thetas,file=paste0(popn,"_mean_diversity_values.txt"),delim="\t",quote="none")
write_delim(basin_divmeans,file=paste0(popn,"_mean_ho_diversity.txt"),delim="\t",quote="none")
write_delim(all_thetas,paste0(popn,"thetas_raw.txt"),delim="\t",quote="none")
write_delim(basin_thetas,paste0(popn,"_mean_tajD.txt"),delim="\t",quote="none")

ts2 <- pivot_longer(all_thetas, cols=c(16,17),values_to="theta", names_to="Theta_Measure")
ts2$Theta_Measure[ts2$Theta_Measure=="tst_persite"] <- "Tajima's Theta"
ts2$Theta_Measure[ts2$Theta_Measure=="wst_persite"] <- "Watterson's Theta"
ylim1 = boxplot.stats(ts2$theta)$stats[c(1, 5)]

ts2 %>% filter(n_snps>1000) %>% ggplot(aes(x=subfacet,y=theta,fill=Theta_Measure)) + geom_boxplot(outlier.alpha=0.01) + coord_cartesian(ylim = ylim1*1.05) + xlab("Population") + ylab("Theta Diversity Value, Sliding Window") + theme_minimal() + theme(axis.text=element_text(angle = 90, vjust = 0.5, hjust=1)) + theme(text=element_text(size=20)) + fill_palette(c("#2ca25f",	"#99d8c9")) + theme(text=element_text(size=20,family="open sans"), axis.text = element_text(size=20),axis.title=element_text(size=20),legend.text = element_text(size=20),legend.title=element_text(size=20))

ggsave(paste0(popn,"_diversity_thetas_boxplots.png"),device="png",dpi=300)

ts2 %>% filter(n_snps>1000) %>% ggplot(aes(x = theta, y = subfacet, fill = subfacet)) + geom_density_ridges() + theme_ridges(font_size=20,) + theme(legend.position = "none",) + xlab("Per-Site Theta Values") +ylab("Population") + fill_palette(c("royalblue","skyblue","pink","pink3")) + xlim(c(-0.005,0.06)) + theme(text=element_text(size=20,family="open sans"), axis.text = element_text(size=18),axis.title=element_text(size=18),legend.text = element_text(size=18),legend.title=element_text(size=18)) + facet_wrap(facets="Theta_Measure")

ggsave(paste0(popn,"_diversity_thetas_ridgeline.png"),device="png",dpi=300)


##calculate smoothed averages##
sliding_ho <- calc_smoothed_averages(x = pop_hofilt, facets = "Population", sigma = 50, step =25)
sliding_ho_stats <- get.snpR.stats(sliding_ho, facets="Population",stats=c("ho","pi"))
single_ho <- sliding_ho_stats$single.window
single_pi <- sliding_ho_stats$single.window
#divide by number of interrogated sites for autosomal ho
single_ho$auto_ho <- single_ho$ho/single_ho$n_snps

single_ho %>% ggplot(aes(x = auto_ho, y = subfacet, fill = subfacet)) + geom_density_ridges() + theme_ridges(font_size=20) + theme(legend.position = "none",text=element_text(family="open sans",size=20)) + xlab("Observed Heterozygosity") +ylab("Population") + fill_palette(c("royalblue","skyblue","pink","pink3")) + xlim(c(0,0.000007))

ggsave(paste0(popn,"_diversity_ho_ridgeline.png"),device="png",dpi=300)

###ibd
##

pop2 <- calc_isolation_by_distance(
  pop_elsefilt,
  facets = "Population",
  x_y = c("long", "lat"),
  genetic_distance_method = "Edwards",
  interpolate = "bernoulli",
)

ibd2 <- get.snpR.stats(pop2, "Population", stats=c("isolation_by_distance","geographic_distance"))

ibd2

###Fst
fst <- calc_pairwise_fst(pop_elsefilt, facets="Population")
fst2 <- get.snpR.stats(fst,"Population",stats="fst")

plot_pairwise_fst_heatmap(fst,facets="Population",,viridis.option="mako",lab_lower=TRUE) + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) + theme(text=element_text(size=22,family="open sans"),axis.title=element_text(size=1)) + geom_label(ggplot2::aes(label = round(weighted_mean_fst, 3), x = p2, y = p1), fill = "white",size=14, family="open sans")

ggsave(paste0(popn,"_fst_table.png"),device="png",dpi=300)

oregon_m <- unique(data.frame("Population"=samp_meta$Population,"long"=samp_meta$long,"lat"=samp_meta$lat))
d1 <- geodist(oregon_m,paired=TRUE,measure = "geodesic")
#turn matrix into pairwise
colnames(d1) <- oregon_m$Population
row.names(d1) <- oregon_m$Population
d1 <- as.data.frame(d1)
xy <- t(combn(colnames(d1), 2))
dists <- data.frame(xy, dist=d1[xy])
dists$subfacet <- paste0(dists$X1,"~",dists$X2)
dists2 <- dists
dists2$subfacet <- paste0(dists$X2,"~",dists$X1)
oregon_dists <- rbind(dists,dists2)

#I want it in km, rather than m, so divide by 1000
oregon_dists$dist_km <- dists$dist / 1000

oregon_fst_dist <- fst2$weighted.means
oregon_fst_dist <- left_join(oregon_fst_dist,oregon_dists,by="subfacet")
oregon_fst_dist$t_geodist <- log(oregon_fst_dist$dist_km) #take the natural log
oregon_fst_dist$t_fst <- oregon_fst_dist$weighted_mean_fst/(1-oregon_fst_dist$weighted_mean_fst)


###PCA###
pc <- plot_clusters(pop_elsefilt,facets="Population")
pca <- pc$data$pca
popname <- str_to_title(popn)
 
ggplot2::ggplot(pca, aes(PC1, PC2, fill=Population)) + geom_point(shape=21,size=8,stroke=1) +xlab(paste0("PC1 (",pc$pca_loadings[1],"%)")) + ylab(paste0("PC2 (",pc$pca_loadings[2],"%)")) +ggtitle(paste0("VPFS ",popname, " Intra-Site Analysis: All Loci PC1-PC2")) +fill_palette(c("royalblue","skyblue","pink","pink3")) +theme_minimal() +theme(text=element_text(size=22,family="open sans")) 

ggsave(paste0(popn,"_pca_pc1vpc2.png"),device="png",dpi=300)

ggplot2::ggplot(pca, aes(PC1, PC3, fill=Population)) + geom_point(shape=21,size=8,stroke=1) +xlab(paste0("PC1 (",pc$pca_loadings[1],"%)")) + ylab(paste0("PC3 (",pc$pca_loadings[3],"%)")) +ggtitle(paste0("VPFS ",popname, " Intra-Site Analysis: All Loci PC1-PC3")) +fill_palette(c("royalblue","skyblue","pink","pink3")) +theme_minimal() +theme(text=element_text(size=22,family="open sans")) 

ggsave(paste0(popn,"_pca_pc1vpc3.png"),device="png",dpi=300)

###reformat for Bayesass###
pop_morefilt <- filter_snps(x = pop,maf = 0.05, hf_hets = 0.6,min_ind =  0.99, min_loci = 0.5, re_run = "partial", non_poly = TRUE, bi_al = TRUE)

pop_forbayes <- as.data.frame(pop_morefilt)
pop_fb_samp <- sample.meta(pop_morefilt)
pop_fb_snps <- snp.meta(pop_morefilt)
pop_fb_snps$chr_pos <- paste0(pop_fb_snps$chromo,"_",pop_fb_snps$position)
rownames(pop_forbayes) <- pop_fb_snps$chr_pos
colnames(pop_forbayes) <- pop_fb_samp$sample
pop_forbayes$allele <- rownames(pop_forbayes)
test2 <- data.frame(pop_forbayes)
test3 <- pivot_longer(test2, cols=c(1:(ncol(test2)-1)),names_to="sample")
test4 <- right_join(samp_meta,test3,by="sample")
test4$a1 <- str_split_i(test4$value,"",1)
test4$a2 <- str_split_i(test4$value,"",2)
test4$a1[test4$a1 =="N"] <- 0
test4$a2[test4$a2 =="N"] <- 0
test5 <- data.frame("indID"=test4$sample,"PopulationID"=test4$Population,"locID"=test4$allele,"allele1"=test4$a1,"allele2"=test4$a2)
write_delim(test5,paste0(popn,"_for_ba3_snpr.txt"),delim=" ")
##
##njtree

library("ape")
df2 <- data.frame(pop_elsefilt)
df3 <- as.data.frame(t(df2))
row.names(df3) <- sample.meta(pop_elsefilt)$sample
colnames(df3) <- paste0(snp.meta(pop_elsefilt)$chromo,"_",snp.meta(pop_elsefilt)$position)
t1 <- df2genind(df3, pop=sample.meta(pop_elsefilt)$Population,ncode=2,NA.char="NN")
X <- tab(t1, NA.method="mean")
D <- dist(X)
tre <- nj(D)
#levels(t1@pop) <- c("Oregon_A","Oregon_B","Oregon_C","Oregon_D")
h2 <- rev(c("royalblue","skyblue","pink","pink3"))
myCol <- h2[as.integer(pop(t1))]
par(bg = "white",family="open sans")
plot(tre, type = "unr", show.tip.lab = FALSE)
tiplabels(col = "black", pch = 21, bg=myCol,cex=3.5)
poplist <- levels(t1@pop)
mylegcol <- unique(myCol)
legend(-30,100,legend=poplist, fill=mylegcol, cex=1, title="Population", bty="n")
ggsave(paste0(popn,"_njtree.png"), device="png", dpi=200)
```

```{r rockpools}
#define local name
popn="rockpools"

#import data
snp_meta_in <- paste0("bly_2024_",popn,".mafs")
sample_meta_in <- paste0("bly_2024_",popn,"_meta.txt")
gen <- read.delim(paste0("bly_2024_",popn,".geno"), header=FALSE)
sm<- read.delim(snp_meta_in)
snp_meta <- sm[,1:4]
rm(sm)
gen <- gen[,3:(ncol(gen)-1)]
samp_meta <- read.delim(sample_meta_in,header=TRUE)

#format as snpR
pop <- import.snpR.data(gen,sample.meta = samp_meta,snp.meta = snp_meta ,mDat = "NN")

##filter
pop_hofilt <- filter_snps(x=pop, hf_hets = 0.6, min_ind=0.5,non_poly=FALSE)

pop_elsefilt <- filter_snps(x = pop, maf = 0.05, hf_hets = 0.6, min_ind =  0.8, min_loci = 0.5, re_run = "partial", non_poly = TRUE, bi_al = TRUE) 

##diversity##
##

pop_hofilt <- calc_pi(pop_hofilt, "Population")
pop_hofilt <- calc_ho(pop_hofilt, "Population")
pop_hofilt <- calc_he(pop_hofilt, "Population")
pop_hofilt <- calc_private(pop_hofilt, "Population")
pop_hofilt <- calc_tajimas_d(pop_hofilt, "Population.chromo",sigma=50,step=25)
stats <- get.snpR.stats(pop_hofilt, "Population", stats = c("pi", "ho", "he")) 
thetas <- get.snpR.stats(pop_hofilt, "Population.chromo", stats="tajimas_d")

#format and prep for graphics
basin_divmeans <- stats$weighted.means
basin_divmeans$ho_aut <- basin_divmeans$weighted_mean_ho / nsnps(pop_hofilt)
basin_divmeans$he_aut <- basin_divmeans$weighted_mean_he / nsnps(pop_hofilt)
basin_thetas <- filter(thetas$weighted.means,snp.subfacet==".OVERALL_MEAN")

all_thetas <- thetas$single.window
all_thetas$wst_persite <- all_thetas$ws.theta / all_thetas$n_snps
all_thetas$tst_persite <- all_thetas$ts.theta / all_thetas$n_snps
all_thetas$D <- as.numeric(all_thetas$D)
mean_thetas <- all_thetas %>% group_by(subfacet) %>% filter(n_snps>1000) %>% summarise(Taj_D=mean(D),mean_ttheta_persite=mean(tst_persite),sd_ttheta_persite=sd(tst_persite),mean_wtheta_persite=mean(wst_persite),sd_wtheta_persite=sd(wst_persite))

#write the summary
write_delim(mean_thetas,file=paste0(popn,"_mean_diversity_values.txt"),delim="\t",quote="none")
write_delim(basin_divmeans,file=paste0(popn,"_mean_ho_diversity.txt"),delim="\t",quote="none")
write_delim(all_thetas,paste0(popn,"thetas_raw.txt"),delim="\t",quote="none")
write_delim(basin_thetas,paste0(popn,"_mean_tajD.txt"),delim="\t",quote="none")

ts2 <- pivot_longer(all_thetas, cols=c(16,17),values_to="theta", names_to="Theta_Measure")
ts2$Theta_Measure[ts2$Theta_Measure=="tst_persite"] <- "Tajima's Theta"
ts2$Theta_Measure[ts2$Theta_Measure=="wst_persite"] <- "Watterson's Theta"
ylim1 = boxplot.stats(ts2$theta)$stats[c(1, 5)]

ts2 %>% filter(n_snps>1000) %>% ggplot(aes(x=subfacet,y=theta,fill=Theta_Measure)) + geom_boxplot(outlier.alpha=0.01) + coord_cartesian(ylim = ylim1*1.05) + xlab("Population") + ylab("Theta Diversity Value, Sliding Window") + theme_minimal() + theme(axis.text=element_text(angle = 90, vjust = 0.5, hjust=1)) + theme(text=element_text(size=20)) + fill_palette(c("#2ca25f",	"#99d8c9")) + theme(text=element_text(size=20,family="open sans"), axis.text = element_text(size=20),axis.title=element_text(size=20),legend.text = element_text(size=20),legend.title=element_text(size=20))

ggsave(paste0(popn,"_diversity_thetas_boxplots.png"),device="png",dpi=300)

ts2 %>% filter(n_snps>1000) %>% ggplot(aes(x = theta, y = subfacet, fill = subfacet)) + geom_density_ridges() + theme_ridges(font_size=20,) + theme(legend.position = "none",) + xlab("Per-Site Theta Values") +ylab("Population") + fill_palette(c("#CAB2D6","#8968CD")) + xlim(c(-0.005,0.06)) + theme(text=element_text(size=20,family="open sans"), axis.text = element_text(size=18),axis.title=element_text(size=18),legend.text = element_text(size=18),legend.title=element_text(size=18)) + facet_wrap(facets="Theta_Measure")

ggsave(paste0(popn,"_diversity_thetas_ridgeline.png"),device="png",dpi=300)


##calculate smoothed averages##
sliding_ho <- calc_smoothed_averages(x = pop_hofilt, facets = "Population", sigma = 50, step =25)
sliding_ho_stats <- get.snpR.stats(sliding_ho, facets="Population",stats=c("ho","pi"))
single_ho <- sliding_ho_stats$single.window
single_pi <- sliding_ho_stats$single.window
#divide by number of interrogated sites for autosomal ho
single_ho$auto_ho <- single_ho$ho/single_ho$n_snps

single_ho %>% ggplot(aes(x = auto_ho, y = subfacet, fill = subfacet)) + geom_density_ridges() + theme_ridges(font_size=20) + theme(legend.position = "none",text=element_text(family="open sans",size=20)) + xlab("Observed Heterozygosity") +ylab("Population") + fill_palette(c("#CAB2D6","#8968CD")) + xlim(c(0,0.000007))

ggsave(paste0(popn,"_diversity_ho_ridgeline.png"),device="png",dpi=300)

###skip IBD for Rockpools because there are only 2 pops
##

###Fst
fst <- calc_pairwise_fst(pop_elsefilt, facets="Population")
fst2 <- get.snpR.stats(fst,"Population",stats="fst")

plot_pairwise_fst_heatmap(fst,facets="Population",viridis.option="mako",lab_lower=FALSE) + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) + theme(text=element_text(size=22,family="open sans"),axis.title=element_text(size=1)) 

ggsave(paste0(popn,"_fst_table.png"),device="png",dpi=300)

rockpools_m <- unique(data.frame("Population"=samp_meta$Population,"long"=samp_meta$long,"lat"=samp_meta$lat))
d1 <- geodist(rockpools_m,paired=TRUE,measure = "geodesic")
#turn matrix into pairwise
colnames(d1) <- rockpools_m$Population
row.names(d1) <- rockpools_m$Population
d1 <- as.data.frame(d1)
xy <- t(combn(colnames(d1), 2))
dists <- data.frame(xy, dist=d1[xy])
dists$subfacet <- paste0(dists$X1,"~",dists$X2)
dists2 <- dists
dists2$subfacet <- paste0(dists$X2,"~",dists$X1)
rockpools_dists <- rbind(dists,dists2)

#I want it in km, rather than m, so divide by 1000
rockpools_dists$dist_km <- dists$dist / 1000

rockpools_fst_dist <- fst2$weighted.means
rockpools_fst_dist <- left_join(rockpools_fst_dist,rockpools_dists,by="subfacet")
rockpools_fst_dist$t_geodist <- log(rockpools_fst_dist$dist_km) #take the natural log
rockpools_fst_dist$t_fst <- rockpools_fst_dist$weighted_mean_fst/(1-rockpools_fst_dist$weighted_mean_fst)


###PCA###
pc <- plot_clusters(pop_elsefilt,facets="Population")
pca <- pc$data$pca
popname <- str_to_title(popn)
 
ggplot2::ggplot(pca, aes(PC1, PC2, fill=Population)) + geom_point(shape=21,size=8,stroke=1) +xlab(paste0("PC1 (",pc$pca_loadings[1],"%)")) + ylab(paste0("PC2 (",pc$pca_loadings[2],"%)")) +ggtitle(paste0("VPFS ",popname, " Intra-Site Analysis: All Loci PC1-PC2")) +fill_palette(c("#CAB2D6","#8968CD")) + theme_minimal() +theme(text=element_text(size=22,family="open sans")) 

ggsave(paste0(popn,"_pca_pc1vpc2.png"),device="png",dpi=300)

ggplot2::ggplot(pca, aes(PC1, PC3, fill=Population)) + geom_point(shape=21,size=8,stroke=1) +xlab(paste0("PC1 (",pc$pca_loadings[1],"%)")) + ylab(paste0("PC3 (",pc$pca_loadings[3],"%)")) +ggtitle(paste0("VPFS ",popname, " Intra-Site Analysis: All Loci PC1-PC3")) +fill_palette(c("#CAB2D6","#8968CD")) + theme_minimal() +theme(text=element_text(size=22,family="open sans")) 

ggsave(paste0(popn,"_pca_pc1vpc3.png"),device="png",dpi=300)

###reformat for Bayesass###
pop_morefilt <- filter_snps(x = pop,maf = 0.05, hf_hets = 0.6,min_ind =  0.99, min_loci = 0.5, re_run = "partial", non_poly = TRUE, bi_al = TRUE)

pop_forbayes <- as.data.frame(pop_morefilt)
pop_fb_samp <- sample.meta(pop_morefilt)
pop_fb_snps <- snp.meta(pop_morefilt)
pop_fb_snps$chr_pos <- paste0(pop_fb_snps$chromo,"_",pop_fb_snps$position)
rownames(pop_forbayes) <- pop_fb_snps$chr_pos
colnames(pop_forbayes) <- pop_fb_samp$sample
pop_forbayes$allele <- rownames(pop_forbayes)
test2 <- data.frame(pop_forbayes)
test3 <- pivot_longer(test2, cols=c(1:(ncol(test2)-1)),names_to="sample")
test4 <- right_join(samp_meta,test3,by="sample")
test4$a1 <- str_split_i(test4$value,"",1)
test4$a2 <- str_split_i(test4$value,"",2)
test4$a1[test4$a1 =="N"] <- 0
test4$a2[test4$a2 =="N"] <- 0
test5 <- data.frame("indID"=test4$sample,"PopulationID"=test4$Population,"locID"=test4$allele,"allele1"=test4$a1,"allele2"=test4$a2)
write_delim(test5,paste0(popn,"_for_ba3_snpr.txt"),delim=" ")
##
##njtree

library("ape")
df2 <- data.frame(pop_elsefilt)
df3 <- as.data.frame(t(df2))
row.names(df3) <- sample.meta(pop_elsefilt)$sample
colnames(df3) <- paste0(snp.meta(pop_elsefilt)$chromo,"_",snp.meta(pop_elsefilt)$position)
t1 <- df2genind(df3, pop=sample.meta(pop_elsefilt)$Population,ncode=2,NA.char="NN")
X <- tab(t1, NA.method="mean")
D <- dist(X)
tre <- nj(D)
h2 <- c("#CAB2D6","#8968CD")
myCol <- h2[as.integer(pop(t1))]
par(bg = "white",family="open sans")
plot(tre, type = "unr", show.tip.lab = FALSE)
tiplabels(col = "black", pch = 21, bg=myCol,cex=3.5)
poplist <- levels(t1@pop)
mylegcol <- unique(myCol)
legend(-20,80,legend=poplist, fill=mylegcol, cex=1, title="Population", bty="n")
```


```{r distfst}

list_of_dists <- mget(ls(pattern="fst_dist"))

local_dist <- rbind(merced_fst_dist,oregon_fst_dist,sac_fst_dist,rockpools_fst_dist)

ggplot(local_dist,aes(x=t_geodist,y=t_fst))+geom_point()+geom_smooth(color="#4a90e2",fill="#a5deba") + theme_pubr() + xlab("Natural Log of Geographic Distance") + ylab("Fst/(1-Fst)") +theme(text = element_text(size = 20, family="open sans"))

ggsave("local_bly_fst_vs_geog.png",device="png",dpi=300)

local_dist$Comparison_Type <- c("Within Site","Between Sites","Between Sites","Between Sites","Between Sites","Between Sites","Between Sites","Between Sites","Between Sites","Between Sites","Between Sites","Within Site","Within Site","Between Sites","Between Sites","Between Sites","Between Sites","Between Sites","Within Site","Within Site","Within Site","Within Site","Within Site","Within Site","Within Site","Within Site","Within Site","Within Site","Within Site","Within Site","Within Site","Within Site","Within Site","Within Site","Between Sites","Between Sites","Between Sites","Between Sites","Between Sites","Within Site","Within Site")

local_dist %>% filter(dist_km<11) %>% ggplot(aes(x=dist_km,y=weighted_mean_fst,fill=Comparison_Type)) +geom_point(size=8,stroke=1,shape=21) + xlab("Distance (km)") + ylab("Weighted Mean Pairwise Fst") + theme_minimal() + theme(text=element_text(size=20,family="open sans")) + fill_palette(c("#2ca25f",	"#99d8c9"))

ggsave("local_bly_10km_fst_vs_geog.png",device="png",dpi=300)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
